### 2013-05-17 Docs/architecture/architecture.tex
update to show initial_models
more docs

@@

@@

@@

@@

@@

>>>>

    \item {\tt initial\_models/}

      Simple routines for generating toy initial models in hydrostatic equilibrium.

@@

By separating the layout from the actual data, we can allocate and
destroy data that lives on the grid as needed.

@@

All \fab s in a given \multifab\ have the same number of ghost cells,
but different \multifab s can have different numbers of ghost cells
(or no ghost cells).

@@

The main purpose of this module is to define the Fortran kind {\tt dp\_t}
which is used throughout the code to declare double precision variables.

@@

This module provides descriptive names for a number of common double precision
numbers, e.g.\ {\tt ONE = 1.0\_dp\_t}.  This enhances the readability of
the code.

@@

All MPI calls are wrapped by functions in the {\tt parallel} module.  For
serial jobs, the wrappers simply do the requested operation on processor.
By wrapping the calls, we can easily switch between serial and parallel
builds.
